Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
Big changes

@@

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\!J,\mathcal{S}_1, s_0,
   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
   are open automata with identical holes of the same sort.

@@

\end{mathpar}
 there exist   open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
    \openrule
         {
           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {\alpha_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J'=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\implies$\\
%\hspace{1cm}
 $\bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.
\bigskip

 $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$\\
and
%\hspace{1cm}
 $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

Idea: we define $OT\implies OT$ to check whether an OT is a particular case of another one (refining free action variables and predicates)
 \begin{mathpar}
    \openrule
         {
           \beta_{j}^{j\in J_{x}}, \Pred_{OT},\subst{x_k\leftarrow e_k}^{k\in K}}
          {t \OTarrow {\alpha} t'}\in\mathcal{T}
\implies
    \openrule
         {
           (\beta_{j}\Post)^{j\in J}, \Pred_{OT}\Post\land\Pred,\subst{x_k\leftarrow e_k\Post}^{k\in K}}
         {t \OTarrow {\alpha\Post} {t'}}\in\mathcal{T}
\end{mathpar}

@@

% \TODO{do we want formulas for this?}
 \end{definition}
Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but not between  $\Post_{OT}$ and
$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
We can prove that such a bisimulation si an equivalence relation:

@@

	\noindent
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J \frac{num}{den}	\\
    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}    
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}
\end{definition}
        	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the pNet structure,
	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.

@@

%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},\Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
} 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\qquad \WTDeux
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
 and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
} \WTTrois
\end{mathpar}

@@

\noindent
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
Let $\mathcal{R}$ a relation over
$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
			\Pred\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
			\Post\uplus \Post^2}
{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
	}
	\]

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha^l} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'}^3}}}\] 
where
\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
\left(Pred\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
\end{array}
\]

\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}
\]
Note that we have $s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$
\end{proof}

>>>>

\TODO{prendre soin des posts sur les actions partout}

@@

We take in this article a semantics and logical understanding of these automata. Open automata are closed by a simple form of refinement that allows us to refine the predicate, or substitute any free variable by an expression. More formally, let $\Post$ be any substitution and $\Pred$ any predicate suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and $\vars(t')\cap \dom(\Post)=\emptyset$. Then we have the following implication:

	 \begin{mathpar}
    \openrule
         {
           \set{\beta}, \Pred\,',\Post\,'}
          {t \OTarrow {\alpha} t'}\in\mathcal{T}
\implies
    \openrule
         {
           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\otimes\Post\,'}
         {t \OTarrow {\alpha\subst{\Post}} {t'}}\in\mathcal{T}
\end{mathpar}
\end{definition}

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\!J,\mathcal{S}_1, s_0,
   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
   are open automata with identical holes of the same sort, with disjoint state variables.

@@

\end{mathpar}
 there exist   open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
    \openrule
         {
           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {\alpha_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J'=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\implies$\\
%\hspace{1cm}
 $\bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.
\bigskip

 $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$\\
and
%\hspace{1cm}
 $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

% \TODO{do we want formulas for this?}
 \end{definition}
Classically, $\Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but not between  $\Post_{OT}$ and
$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
We can prove that such a bisimulation si an equivalence relation:

@@

	\noindent
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
    J' = \biguplus_{m\in I_1}\!\! J_m \uplus J	\\
    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j^{j\in J},\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		\beta_j^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}    
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}
\end{definition}
        	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the pNet structure,
	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.

@@

%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},\Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
} 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\qquad \WTDeux
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
 and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3  }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\otimes\Post_1}
\\
\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\otimes \Post_1}\\
\alpha'=\alpha\subst{\Post_1}
}
{
\openrule
         {\set{\gamma}
           ,
		\Pred,
				\Post_3\otimes\Post_2\otimes\Post_1} 
         {s \OTWeakarrow {\alpha'} s'} \in\WT
} \WTTrois
\end{mathpar}

@@

\noindent
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata with disjoint state variables.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
Let $\mathcal{R}$ a relation over
$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.

@@

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\otimes\Post_{OT_x}}\right)$

@@

\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
			\Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 },  
			\Post\uplus \Post^2}
{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
	}
	\]

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'+1}^3}}}\] 
where
\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
\left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
\end{array}
\]

\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}
\]
Note that we have $s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\

Note also that $\Post$ only acts on variables of $P$ while $\Post^1_i$ only acts on state variables of $Q$. A
\end{proof}
